\documentclass[11pt,a4paper]{article}\usepackage{times,hyperref}\usepackage{fullpage}\usepackage{nopageno}\begin{document}\begin{tabular}{rcl}{\Large Toby Dylan Hocking} & nationality: American &phone: +33 1 39 63 54 99\\email: toby.hocking AT inria.fr & birth: 17 March 1984& web: \url{http://cbio.ensmp.fr/~thocking}\end{tabular} \subsection*{Publications, posters, talks}\begin{itemize}\item ``Sustainable package development using documentation generation,'' talk 21 October 2010 for semin-r, the Paris R user group.\item\href{http://www.plosone.org/article/info\%3Adoi\%2F10.1371\%2Fjournal.pone.0011913}{Gautier M, {\bf Hocking~TD}, Foulley JL.A Bayesian Outlier Criterion to Detect SNPs under Selection in LargeData Sets, \emph{PLoS ONE} 5(8): e11913 (2010).}\item ``Visualizingmultivariate data using lattice and direct labels,'' talk 15 October2009 for semin-r, the Paris R user group.\item Sublogo dendrograms:visualizing correlation in biological sequence motifs, posterpresented at\href{http://www.agrocampus-ouest.fr/math/useR-2009/}{useR! 2009}.\item \href{http://www.ncbi.nlm.nih.gov/pubmed/18500334}{Doyon~Y, McCammon~JM, Miller~JC, Faraji~F, Ngo~C,Katibah~GE, Amora~R, {\bf Hocking~TD}, Zhang~L, \mbox{Rebar~EJ}, Gregory~PD,Urnov~FD, Amacher~SL. Heritable targeted gene disruption in zebrafishusing designed zinc-finger nucleases, \emph{Nature~Biotechnology}26, 702-708 (2008).}\end{itemize}\subsection*{Professional and research experience} \label{profexp}\begin{description}\newcommand{\job}[4]{\item[#1, #2]\hrulefill\ #3 \\ #4}\job{Free software developer}{SourceForge.net,  R-Forge.R-project.org}{since November 2007}{  - \href{http://sf.net/projects/django-dataplot/}{Django-dataplot} for  statistical graphics on a web site using R, Python, and  Django.\\ - \href{http://sf.net/projects/gpsdb/}{GPSDB}, a Python  program for making websites for GPS data, and visualizing them using  Google Maps.\\- \href{http://inlinedocs.r-forge.r-project.org/}{inlinedocs} R package for documentation generation based on comments in R code.\\- \href{http://directlabels.r-forge.r-project.org}{directlabels} R package for automatic direct labeling of multicolor plots.\\- \href{http://nicholsonppp.r-forge.r-project.org/}{nicholsonppp} R package for fitting a Bayesian model of evolution.\\- \href{http://sublogo.r-forge.r-project.org/}{sublogo} R package for plotting sublogo dendrograms, for visualizing biological sequence alignment data.\\- \href{https://bugs.r-project.org/bugzilla3/show_bug.cgi?id=14518}{Patched the R interpreter} to support named capture in regular expressions using the PCRE library.}\job{Research assistant}{Sangamo BioSciences, Richmond, CA}{June 2006-- August 2008}{  Performed biochemical assays to determine sequence specificity of  DNA-binding proteins.  \\   Designed protein linkers for optimal  nuclease activity and specificity. \\   Deployed an internal web  database for visualizing and comparing proteins and experiments.}\job{General manager}{Open Computing Facility, Berkeley, CA}{October 2005 -- May 2006}{Managed finances, personnel, and public relations for this student computercenter of over 10,000 users.  \\Installed and maintained software packages and helped users withtechnical difficulties.}\end{description}\subsection*{Programming skills}Fortran, C, C++, Perl, Python, regular expressions, Emacs-Lisp, R,SAS, HTML, SQL, PHP, CSS, \LaTeX, Subversion, Mercurial, Debiansystems administration.\subsection*{Language skills: English (mother tongue), French (fluent)}\subsection*{Education}\begin{description}\item[Ecole Normale Sup\'erieure, Paris, France, October 2009 -- 2012]Doctoral research in statistical learning applied to computer visionand bioinformatics with advisors Francis Bach and Jean-Philippe Vert.\item[Pierre and Marie Curie University, Paris, France, September2009] Masters of statistics with internship at INRA in\href{http://nicholsonppp.r-forge.r-project.org/}{Bayesian statisticsapplied to models of domestic animal evolution} with advisors MathieuGautier and Jean-Louis Foulley.\item[UC Berkeley, Spring 2006] Bachelors in molecular and cell  biology and statistics. Honors thesis with advisor Terry Speed on  chromosomal copy number analysis using SNP microarrays.\end{description}\subsection*{Hobbies}Playing saxophone and clarinet (since 1994), playing soccer (since 2006),bicycle riding and touring (since 2007).\end{document}